Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-19 paper/paper.discussion.tex
Add future work paragraph to discussion

Our tool is also employed at the Infectious Diseases Department at St. Michael's Hospital. It provides a simple and easy-to-use user interface that can be used by any hospital staff to generate schedules well in advance. We compare the manually created schedule at St. Michael's Hospital to the optimal schedule generated with the help of our tool. We see adherence to all required hard constraints in the generated schedule, while some of them were overlooked in the manual schedule. Moreover, we see a much better fulfillment of clinician requests than in the manual schedule. This reinforces the idea that it is vital to employ automated tools when generating schedules in hospital departments, to reduce human error, balance the work-load of clinicians and improve the service provided to patients.

>>>>

Our tool is also employed at the Infectious Diseases Department at St. Michael's Hospital. It provides a simple and easy-to-use user interface that can be used by any hospital staff to generate schedules well in advance. We compare the manually created schedule at St. Michael's Hospital to the optimal schedule generated with the help of our tool. We see adherence to all required hard constraints in the generated schedule, while some of them were overlooked in the manual schedule. Moreover, we see a much better fulfillment of clinician requests than in the manual schedule. This reinforces the idea that it is vital to employ automated tools when generating schedules in hospital departments, to reduce human error, balance the work-load of clinicians and improve the service provided to patients. \\

In future work, we can look first and foremost into improving the runtime of the tool by modifying constraints and objectives, so that it can be used in larger departments offering multiple services for their patients. On top of that, we can introduce new objectives that incorporate additional clinician preferences and allow for better distribution of work-load. However, since our ultimate goal is to maintain a ILP formulation, care must be taken not to overly complicate the model and risk running into additional time complexity issues.
